---
title: "My first RMarkdown"
author: "Zeynep"
date: "12/03/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# header
## R Markdown

This is an **R Markdown** document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:
### smaller topic

####even smaller topic
*bold* **italic**

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:
```{r}
print("hello world")
```

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
Try  
Making  
your  
own  
bullet  
list!  

